---
title: "Breakpoints"
output: html_document
date: "2025-07-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
library(ggpubr) # for ggdensity
library(segmented) #for breakpoints
library(tidyverse)
```


## Set up data

site characteristics

```{r}

Site_code_number <- data.frame(Site_code = c("CS1", "CS2", "CP1", "CP2", "CC1", "CC2", "CC3", "CC4", "C50"),
                               Site_number = c(101, 100, 98, 96, 94, 92, 90, 88, 50))

## bring in distances and site class table from google sheets; have to redownload locally each time 
distances <- read.csv("C:/Users/dwh18/Downloads/2024 spatial sampling - Distances.csv") |> 
  mutate(Date = mdy(Date)) |> 
  dplyr::select(-c(13,14)) |> 
  pivot_longer(-c(1,11,12), names_to = "Site_code", values_to = "Distance_ft") |> 
  filter(!Site_code == "C1") 


site_class <- read.csv("C:/Users/dwh18/Downloads/2024 spatial sampling - Sites_Class.csv") |> 
  dplyr::select(-X, -Key) |> 
  mutate(Date = mdy(Date)) |> 
  pivot_longer(-c(1), names_to = "Site_code", values_to = "Site_Class") |> 
  mutate(Site_Class = ifelse(Site_Class %in% c("S", "S "), "Stream", Site_Class),
         Site_Class = ifelse(Site_Class %in% c("P", "P "), "Pool", Site_Class),
         Site_Class = ifelse(Site_Class == "C", "Cove", Site_Class),
         Site_Class = ifelse(Site_Class == "L", "Pelagic", Site_Class))

```


read in data sets

```{r}
#### Isotopes ###
iso24 <- read.csv("../Water_Isotopes/isotopes_named.csv") |> 
  rename(Site = Site_number) |> 
  filter(Site != 51) |> 
    filter(Site != 94) |> 
  mutate(Date = mdy(Date))


#### EEMS ###
eems24 <- read.csv("../EEMs_Results_2024.csv")

eems <- eems24 |> 
    mutate(Date = mdy(Date),
           Date = ifelse(Date == ymd("2024-08-15"), ymd("2024-08-14"), Date),
           Date = ifelse(Date == ymd("2025-02-17"), ymd("2025-02-26"), Date),
           Date = as.Date(Date)) |> 
    filter(!Date %in% c(ymd("2024-07-31"), ymd("2024-08-01"))) |> 
    filter(!NOTES %in% c("PART", "FRIDGE_TEST")) |> 
  filter(Site != 94) |> 
  rename(HIX = HIX.,
         BIX = BIX.,
         FI = FI.,
         A = A.,
         peakT = T.,
         AT = A.T.) |>  #### can just change the rename here for what value you want to look at
  dplyr::select(Site, Depth_m, Date, HIX, BIX, FI, A, peakT, AT, a254, a350) |> 
  group_by(Site, Depth_m, Date) |> 
  summarise(HIX_mean = mean(HIX, na.rm = T),
            HIX_min = min(HIX, na.rm = T),
            HIX_max = max(HIX, na.rm = T),
            BIX_mean = mean(BIX, na.rm = T),
            BIX_min = min(BIX, na.rm = T),
            BIX_max = max(BIX, na.rm = T),
            FI_mean = mean(FI, na.rm = T),
            A_mean = mean(A, na.rm = T),
            T_mean = mean(peakT, na.rm = T),
            AT_mean = mean(AT, na.rm = T),
            a254_mean = mean(a254, na.rm = T),
            a350_mean = mean(a350, na.rm = T)
            ) |> 
  mutate(Rep = ifelse(HIX_mean != HIX_min, "Y", "N"))

#### chem 
edi_chem <- read.csv("https://pasta.lternet.edu/package/data/eml/edi/199/13/3f09a3d23b7b5dd32ed7d28e9bc1b081" )

doc <- edi_chem |> 
  filter(Reservoir == "CCR",
         DateTime > ymd("2024-05-01")) |> 
  mutate(Date = as.Date(DateTime)) |> 
  filter(!Date %in% c(ymd("2024-07-31"), ymd("2024-08-01"))) |> 
  select(Site, Depth_m, Date, DOC_mgL, DN_mgL, NO3NO2_ugL, NH4_ugL, SRP_ugL) |>
  group_by(Site, Depth_m, Date) |>
  summarise(DOC_mean = mean(DOC_mgL, na.rm = T),
            DOC_min = min(DOC_mgL, na.rm = T),
            DOC_max = max(DOC_mgL, na.rm = T),
            DN_mean = mean(DN_mgL, na.rm = T),
            DN_min = min(DN_mgL, na.rm = T),
            DN_max = max(DN_mgL, na.rm = T),
            PO4_mean = mean(SRP_ugL, na.rm = T),
            PO4_min = min(SRP_ugL, na.rm = T),
            PO4_max = max(SRP_ugL, na.rm = T),
            NH4_mean = mean(NH4_ugL, na.rm = T),
            NH4_min = min(NH4_ugL, na.rm = T),
            NH4_max = max(NH4_ugL, na.rm = T),
            NO3_mean = mean(NO3NO2_ugL, na.rm = T),
            NO3_min = min(NO3NO2_ugL, na.rm = T),
            NO3_max = max(NO3NO2_ugL, na.rm = T)
                        ) |>
  mutate(Rep = ifelse(DOC_mean != DOC_min, "Y", "N")) |> 
  mutate(Site = as.numeric(Site))



#### Bring data together ###
chem <- left_join(doc, eems, by = c("Date", "Depth_m", "Site")) |> 
  left_join(iso24, by = c("Date", "Depth_m", "Site")) |> 
  mutate(Site_code = ifelse(Site == 101, "S1", NA),
         Site_code = ifelse(Site == 100, "S2", Site_code),
         Site_code = ifelse(Site == 98, "P1", Site_code),
         Site_code = ifelse(Site == 96, "P2", Site_code),
         Site_code = ifelse(Site == 94, "C1", Site_code),
         Site_code = ifelse(Site == 92, "C2", Site_code),
         Site_code = ifelse(Site == 90, "C3", Site_code),
         Site_code = ifelse(Site == 88, "C4", Site_code),
         Site_code = ifelse(Site == 50, "C50", Site_code)) |> 
  left_join(distances, by = c("Site_code", "Date")) |> 
  left_join(site_class, by = c("Site_code", "Date")) |> 
  mutate(Distance = Distance_ft*0.3048,
         Dry_start = Dry_start*0.3048,
         Dry_end = Dry_end*0.3048) |> 
  mutate(Site_Class = ifelse(Site_Class == "Pool", "Backwater", Site_Class)) |> 
  mutate(Site_Type_static = ifelse(Site %in% c(50,88), "Pelagic", NA),
         Site_Type_static = ifelse(Site %in% c(90,92), "Cove", Site_Type_static),
         Site_Type_static = ifelse(Site %in% c(96,98), "Backwater", Site_Type_static),
         Site_Type_static = ifelse(Site %in% c(100,101), "Stream", Site_Type_static)
  ) |> 
  filter(!Date %in% c(ymd("2024-07-31"), ymd("2024-08-01"))) |> 
  mutate(DON_mean = DN_mean - ((NO3_mean + NH4_mean)/1000)) |> 
  mutate(SUVA254 = a254_mean / DOC_mean) |> 
  mutate(D_excess = d2H_VSMOW - 8*d18O_VSMOW) |> 
  dplyr::select(Reservoir, Site, Site_code, Site_Class, Site_Type_static, 
                Depth_m, Date, Distance, Dry_start, Dry_end, 
                FI_mean, HIX_mean, BIX_mean, T_mean, A_mean, AT_mean, a254_mean, a350_mean, SUVA254,
                DOC_mean, DN_mean, DON_mean, PO4_mean, NO3_mean, NH4_mean,
                d18O_VSMOW, d2H_VSMOW, D_excess)


rm(distances, edi_chem, doc, eems,eems24, iso24)


```



## Normality test

```{r}
#### normality
  ##https://www.sthda.com/english/wiki/normality-test-in-r

ggdensity(chem$BIX_mean, xlab = "BIX", main = "Density plot of BIX in CCR")
shapiro.test(chem$BIX_mean) # p-values < 0.05 means data is not normally distributed
ggdensity(chem$DOC_mean, xlab = "DOC (mg/L)", main = "Density plot of DOC in CCR")
shapiro.test(chem$DOC_mean) 
ggdensity(chem$d2H_VSMOW, xlab = "dH2", main = "Density plot of dH2 in CCR")
shapiro.test(chem$d2H_VSMOW) 

```


## Make nice plots of each variable

```{r}

#Faceting
chem |> 
  select(-c(FI_mean, a350_mean)) |> 
  pivot_longer(-c(1:10)) |> 
  ggplot(aes(x = Distance, y = value, fill = Depth_m))+
  geom_point(shape = 21, size = 4) + #shape = 21,
  #geom_smooth()+
  theme_bw()+ theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(x= "Distance from Stream (m)", fill = "Depth (m)")+
  scale_x_continuous(breaks = c(0, 500, 1000, 1500))+ 
    facet_wrap(~name, scales = "free_y")+
  scale_fill_gradient2(low = "red",  high ="blue",
                       midpoint = 6,  guide = "colourbar", breaks = c(3,6,9, 15))



#### just one variable
#BIX  # bix_clean <- 
chem |> 
  ggplot(aes(x = Distance, y = BIX_mean, fill = Depth_m))+
  geom_point(shape = 21, size = 4) + #shape = 21,
  # geom_smooth()+
  theme_bw()+ theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(x= "Distance from Stream (m)", y = "BIX", fill = "Depth (m)",
       shape = "Site Type")+
  scale_x_continuous(breaks = c(0, 500, 1000, 1500))+ 
  scale_fill_gradient2(low = "red",  high ="blue",
                       midpoint = 6,  guide = "colourbar", breaks = c(3,6,9, 15))



```




## Make boxplots across sites for each variable 

how many samples are different site types depending on grouping
```{r}
#changing sites
chem |>   group_by(Site_Class) |> 
  summarise(Count = n()) 

#fixed
chem |>   group_by(Site_Type_static) |> 
  summarise(Count = n()) 

```



Try function for making all the boxplots

```{r}
library(tidyverse)
library(FSA)
library(rcompanion)
library(ggpubr)
library(rlang)

#### Function

make_kruskal_dunn_plot <- function(df, response_var, group_var = "Site_Type_static", level_order = c("Stream", "Backwater", "Cove", "Pelagic")) {
  
  group_sym <- rlang::sym(group_var)
  response_sym <- rlang::sym(response_var)
  
  formula <- as.formula(paste(response_var, "~", group_var))
  kruskal <- kruskal.test(formula, data = df)
  dunn <- FSA::dunnTest(formula, data = df)
  dunn_letters <- dunn$res
  
  dunn_letters_list <- rcompanion::cldList(
    comparison = dunn_letters$Comparison,
    p.value = dunn_letters$P.adj,
    threshold = 0.05
  )
  
  df_plot <- df %>%
    left_join(dunn_letters_list, by = setNames("Group", group_var))
  
  # Calculate dynamic label position
  y_max <- max(df[[response_var]], na.rm = TRUE)
  label_y <- y_max + 0.01 * abs(y_max)  # Add 10% buffer above max
  
  p <- ggplot(df_plot, aes(x = factor(!!group_sym, levels = level_order), y = !!response_sym)) +
    geom_boxplot(outlier.alpha = 0) +
    geom_jitter(width = 0.2) +
    stat_compare_means(method = "kruskal.test", label.y = label_y * 0.9, label.x = 1.3, size = 4) +
    geom_text(aes(label = Letter), y = label_y, size = 5) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          text = element_text(size = 16),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
    labs(x = "Site Type (Static)", y = response_var)
  
  return(p)
}


#### Run function 
response_vars <- c(
                   "BIX_mean", "HIX_mean", "AT_mean", "SUVA254", 
                   "DOC_mean", "DN_mean", "DON_mean",
                   "NH4_mean", "NO3_mean", "PO4_mean",
                   "d18O_VSMOW", "d2H_VSMOW", "D_excess"
                   )  

# Generate plots for each variable
plots <- lapply(response_vars, function(var) {
  make_kruskal_dunn_plot(chem, response_var = var)
})

# Optionally name the plots
names(plots) <- response_vars


#### Make plots 

#view just one
plots[["DOC_mean"]]  # Or use gridExtra::grid.arrange() to show multiple
plots$BIX_mean

#make a few plots in groups 
library(gridExtra)
gridExtra::grid.arrange(plots$BIX_mean, plots$HIX_mean, plots$AT_mean, plots$SUVA254, nrow = 1) #EEM
gridExtra::grid.arrange(plots$DOC_mean, plots$DON_mean, nrow = 1) #DOM
gridExtra::grid.arrange(plots$NO3_mean, plots$NH4_mean, plots$DN_mean, plots$PO4_mean, nrow = 1) #Nutrients
gridExtra::grid.arrange(plots$d18O_VSMOW, plots$d2H_VSMOW, plots$D_excess, nrow = 1) #Isotopes


#plot all plots at once; too busy for all 13
library(patchwork)
wrap_plots(plots) #makes all the plots


```



## Breakpoints 

Trying function to make these 

```{r}

library(tidyverse)
library(segmented)

##### Function

plot_segmented_breakpoint <- function(df, response_var, predictor_var = "Distance", fill_var = "Depth_m", psi_init = NULL) {
  response_sym <- rlang::sym(response_var)
  predictor_sym <- rlang::sym(predictor_var)
  fill_sym <- rlang::sym(fill_var)

  # Use median as default psi if not provided
  if (is.null(psi_init)) {
    psi_init <- quantile(df[[predictor_var]], probs = 0.5, na.rm = TRUE)
  }

  # Base scatter plot
  base_plot <- ggplot(df, aes(x = !!predictor_sym, y = !!response_sym, fill = !!fill_sym)) +
    geom_point(shape = 21, size = 4) +
    theme_bw() +
    theme(legend.position = "top", text = element_text(size = 18),
          panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    labs(x = paste(predictor_var, "(m)"), y = response_var, fill = paste(fill_var, "(m)")) +
    scale_x_continuous(breaks = c(0, 500, 1000, 1500)) +
    scale_fill_gradient2(low = "red", high = "blue", midpoint = 6,
                         guide = "colourbar", breaks = c(3, 6, 9, 15))

  # Fit linear model
  lm_fit <- lm(as.formula(paste(response_var, "~", predictor_var)), data = df)

  # Try segmented fit
  seg_fit <- tryCatch({
    segmented(lm_fit, seg.Z = as.formula(paste("~", predictor_var)), psi = psi_init)
  }, error = function(e) {
    warning(paste("Segmented fit failed for", response_var, ":", e$message))
    return(NULL)
  })

  # If segmented failed, return base plot with note
  if (is.null(seg_fit)) {
    return(base_plot + ggtitle(paste(response_var, "(segmented fit failed)")))
  }

  # Extract fitted values and breakpoints
  fitted_vals <- fitted(seg_fit)
  df_fitted <- data.frame(Distance = df[[predictor_var]], Fitted = fitted_vals)
  breakpoints <- seg_fit$psi[, "Est."]

  # Extract slope and breakpoint summary
  slope_info <- slope(seg_fit)[[predictor_var]]
  bp_text <- paste0("Breakpoint at ", round(breakpoints, 1), " m\n",
                    "Slope 1: ", round(slope_info[1, "Est."], 3), "\n",
                    "Slope 2: ", round(slope_info[2, "Est."], 3))

  # Dynamic label position
  y_max <- max(df[[response_var]], na.rm = TRUE)
  label_y <- y_max + 0.1 * abs(y_max)

  # Final plot
  final_plot <- base_plot +
    geom_vline(xintercept = breakpoints, linetype = "dashed", size = 1.5) +
    geom_line(data = df_fitted, aes(x = Distance, y = Fitted), size = 1, inherit.aes = FALSE) 
    #annotate("text", x = breakpoints + 100, y = label_y, label = bp_text, hjust = 0, size = 5)

  return(final_plot)
}


#### Run Function

# List of response variables to analyze
response_vars <- c(
                   "BIX_mean", "HIX_mean", "AT_mean", "SUVA254", 
                   "DOC_mean", "DN_mean", "DON_mean",
                   "NH4_mean", "NO3_mean", "PO4_mean",
                   "d18O_VSMOW", "d2H_VSMOW", "D_excess"
                   )  

# Generate segmented plots for each variable
segmented_plots <- lapply(response_vars, function(var) {
  plot_segmented_breakpoint(chem, response_var = var)
})

names(segmented_plots) <- response_vars


#### View plots 

#show all plots
library(patchwork)
wrap_plots(segmented_plots, ncol = 3)

#make a few plots in groups 
library(gridExtra)
#EEMs
gridExtra::grid.arrange(segmented_plots$BIX_mean, segmented_plots$HIX_mean, 
                        segmented_plots$AT_mean, segmented_plots$SUVA254, nrow = 1) #EEM
#DOM
gridExtra::grid.arrange(segmented_plots$DOC_mean, segmented_plots$DON_mean, nrow = 1) #DOM
#Nuts
gridExtra::grid.arrange(segmented_plots$NO3_mean, segmented_plots$NH4_mean, 
                        segmented_plots$DN_mean, segmented_plots$PO4_mean, nrow = 1) #Nutrients
#Iso
gridExtra::grid.arrange(segmented_plots$d18O_VSMOW, segmented_plots$d2H_VSMOW, 
                        segmented_plots$D_excess, nrow = 1) #Isotopes




```

Stack breakpoints and boxplots

```{r}

#### Main variables for MS figure
gridExtra::grid.arrange(segmented_plots$BIX_mean, segmented_plots$DOC_mean, 
                        segmented_plots$D_excess, segmented_plots$NO3_mean,
                        plots$BIX_mean, plots$DOC_mean, plots$D_excess, plots$NO3_mean, nrow = 2)



#### EEMs
gridExtra::grid.arrange(segmented_plots$BIX_mean, segmented_plots$HIX_mean, 
                        segmented_plots$AT_mean, segmented_plots$SUVA254,
                        plots$BIX_mean, plots$HIX_mean, plots$AT_mean, plots$SUVA254, nrow = 2)

#### DOM
gridExtra::grid.arrange(segmented_plots$DOC_mean, segmented_plots$DON_mean,
                        plots$DOC_mean, plots$DON_mean, nrow = 2) #DOM


#### Nutrients
gridExtra::grid.arrange(segmented_plots$NO3_mean, segmented_plots$NH4_mean, 
                        segmented_plots$DN_mean, segmented_plots$PO4_mean,
                        plots$NO3_mean, plots$NH4_mean, plots$DN_mean, plots$PO4_mean, nrow = 2) #Nutrients


#### Isotopes
gridExtra::grid.arrange(segmented_plots$d18O_VSMOW, segmented_plots$d2H_VSMOW, 
                        segmented_plots$D_excess,
                        plots$d18O_VSMOW, plots$d2H_VSMOW, plots$D_excess, nrow = 2) #Isotopes



```



singular breakpoint

```{r}
### BIX

#fit normal linear regression 
my.lm <- lm(BIX_mean ~ Distance, data = chem)
summary(my.lm)

#Run breakpoint
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)

#fit breakpoint segments to distance data
my.fitted <- fitted(my.seg)
my.model <- data.frame(Distance = chem$Distance, BIX_fit = my.fitted)

#get breakpoint lines
my.lines <- my.seg$psi[ , 2]

#plot
chem |> 
  ggplot(aes(x = Distance, y = BIX_mean, fill = Depth_m))+
  geom_point(shape = 21, size = 4) + #shape = 21,
  # geom_smooth()+
  theme_bw()+ theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(x= "Distance from Stream (m)", y = "BIX", fill = "Depth (m)",
       shape = "Site Type")+
  scale_x_continuous(breaks = c(0, 500, 1000, 1500))+ 
  scale_fill_gradient2(low = "red",  high ="blue",
                       midpoint = 6,  guide = "colourbar", breaks = c(3,6,9, 15))+
  #geom_smooth()+
  geom_vline(xintercept = my.lines, linetype = "dashed", size = 1.5) +
  geom_line(data = my.model, aes(x = Distance, y = BIX_fit), size = 1, inherit.aes = FALSE ) 




```

Breakpoint stats for each

```{r}
#BIX
my.lm <- lm(BIX_mean ~ Distance, data = chem)
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)


#HIX
my.lm <- lm(HIX_mean ~ Distance, data = chem)
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)

#DOC
my.lm <- lm(DOC_mean ~ Distance, data = chem)
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)


#DON
my.lm <- lm(DON_mean ~ Distance, data = chem)
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)


#DN
my.lm <- lm(DN_mean ~ Distance, data = chem)
my.seg <- segmented(my.lm,  seg.Z = ~ Distance,  psi = 2 )
summary(my.seg)
my.seg$psi
slope(my.seg)





```







## Put figures together

```{r}
library(patchwork) # | is for side by side

(doc_breakpoint | bix_breakpoint | hix_breakpoint | d2H_breakpoint  ) / 
 (doc_boxplot_type | bix_boxplot_type | hix_boxplot_type | d2H_boxplot_type)
            

##agu abstract
doc_breakpoint | hix_breakpoint



```





## Sensor figures

```{r}
#read in data
sensors <- read.csv("./Sensor_Data_compiled.csv") |> 
   mutate(Site_code = ifelse(Site == 101, "S1", NA),
         Site_code = ifelse(Site == 100, "S2", Site_code),
         Site_code = ifelse(Site == 98, "P1", Site_code),
         Site_code = ifelse(Site == 96, "P2", Site_code),
         Site_code = ifelse(Site == 94, "C1", Site_code),
         Site_code = ifelse(Site == 92, "C2", Site_code),
         Site_code = ifelse(Site == 90, "C3", Site_code),
         Site_code = ifelse(Site == 88, "C4", Site_code),
         Site_code = ifelse(Site == 50, "C50", Site_code)
         ) |> 
  mutate(Date = as.Date(Date)) |> 
    filter(Site != 94) #remove old site C1


sensors <- left_join(sensors, distances, by = c("Site_code", "Date")) |>
    mutate(Distance = Distance_ft*0.3048,
         Dry_start = Dry_start*0.3048,
         Dry_end = Dry_end*0.3048) |> 
  left_join(site_class, by = c("Site_code", "Date")) |> 
  select(Reservoir, Site, Site_code, Site_Class, Date, Distance, Dry_start, Dry_end, Depth_m, Temp_C, DO_mgL, DOsat_percent, SpCond_uScm)


```


all variables by date plot 

```{r}

sensors |> 
  select(-DO_mgL) |> 
  pivot_longer(-c(1:9)) |> 
  # filter(name == "Temp_C") |> 
  ggplot(aes(x = Distance, y = value, fill = Depth_m,
             shape = factor(Site_Class, levels = c("Stream", "Pool", "Cove", "Pelagic"))))+
  geom_rect(aes(xmin = Dry_start, xmax = Dry_end, ymin = -Inf, ymax = Inf), 
            alpha = 0.1, fill = "gray", color = NA )+ #color gets rid of border
  facet_grid(name~Date, scales = "free_y")+
  geom_point(size = 3)+
  theme_bw()+ theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(x= "Distance from Stream (m)",
       shape = "Site Type")+
  scale_x_continuous(breaks = c(0, 500, 1000, 1500))+ #c(250, 750)
  scale_shape_manual(values = c(24, 22, 21, 25))+ #18, 15, 16, 17
  # scale_color_gradient(high = "red", low = "blue") +
  # scale_fill_gradient(high = "red", low = "blue") 
  scale_fill_gradient2(low = "red",  high ="blue",
                       midpoint = 6,  guide = "colourbar", breaks = c(3,6,9, 15, 20))


```


zoom in on shallow sites

```{r}

sensors |> 
  filter(!Site %in% c(50,88,90)) |> 
  select(-DO_mgL) |> 
  pivot_longer(-c(1:9)) |> 
  # filter(name == "Temp_C") |> 
  ggplot(aes(x = Distance, y = value, fill = Depth_m,
             shape = factor(Site_Class, levels = c("Stream", "Pool", "Cove", "Pelagic"))))+
  geom_rect(aes(xmin = Dry_start, xmax = Dry_end, ymin = -Inf, ymax = Inf), 
            alpha = 0.1, fill = "gray", color = NA )+ #color gets rid of border
  facet_grid(name~Date, scales = "free_y")+
  geom_point(size = 3)+
  theme_bw()+ theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  labs(x= "Distance from Stream (m)",
       shape = "Site Type")+
  scale_x_continuous(breaks = c(0, 150, 300))+ #c(250, 750)
  scale_shape_manual(values = c(24, 22, 21, 25))+ #18, 15, 16, 17
  scale_fill_gradient2(low = "red",  high ="blue",
                       midpoint = 0.7,  guide = "colourbar", breaks = c(0,1,2,3))


```





